Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
line breaks

Note that $G(z)$ is a discrete model of a real (and continuous) plant, {\it
i.e.}, a continuous model of the plant must be discretised to obtain the
discrete equivalent coefficients via ZOH
discretisation.

@@

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$ (\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric calculations, or roundoffs in the quantization.
These uncertainties may be parametrically expressed by additive terms, resulting in a uncertain model $\hat{G}(z)$, such that:
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
which will be represented by the following transfer function:
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
Due to the nature of the methods used for stability check in this paper, we require that  the parametric errors in the plant have the same polynomial order as the plant itself (other errors are ensured to fulfil this property in our implementation).

In order to simplify the notations in this paper, we will use a notation based on the coefficients of the polynomials.
Let $\mathcal{P}^{N}$ be a polynomial domain of order $N$
Let $P \in \mathcal{P}^{M,N}$ be a rational polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in \mathcal{P}^{N}$. There is a vector of coefficients 
\begin{equation}
\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
with uncertainty
\begin{equation}
\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.
In the following we may use either notation to represent the functions $G(z)$, $C(z)$, and their respective uncertainties.\\

@@

The ADC and DAC may be abstracted changing the hybrid system in figure~\ref{fig:sampledsystem} to the digital system in figure~\ref{fig:digsystem1} where the parametric uncertainties are represented by $\Delta_p \vec{G}$
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is represented as an additive (output) measurement noise $\nu(z)$, thus $\hat{Y}(z)=Y(z)+\nu(z)$. The measurement noise $\nu(k)$ is enough for represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be obtained reorganizing the equations~\ref{eq:outputfunctions}:
\begin{equation}
\label{eq:outputfunctions2}
\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
\end{equation}
where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
\begin{equation}
\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
\end{equation}

@@

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modelling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties and $\Delta_q \vec{G}$ is the term that reflects the quantisation effects on the plant model. %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.

>>>>

Note that $G(z)$ is a discrete model of a real (and continuous) plant, i.e.,
a continuous model of the plant must be discretised to obtain the discrete
equivalent coefficients via ZOH discretisation.

@@

Uncertainties in $G(z)$ may appear due to uncertainties in $G(s)$
(\emph{i.e.} $\Delta_p{G}_n(s),\Delta_p{G}_d(s)$), errors in the numeric
calculations, or roundoffs in the quantization.  These uncertainties may be
parametrically expressed by additive terms, resulting in a uncertain model
$\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}} : N_G \geq M_G .
\end{equation}
%
Due to the nature of the methods used for stability check in this paper, we
require that the parametric errors in the plant have the same polynomial
order as the plant itself (other errors are ensured to fulfil this property
in our implementation).

In order to simplify the notations in this paper, we will use a notation
based on the coefficients of the polynomials.  Let $\mathcal{P}^{N}$ be a
polynomial domain of order $N$ Let $P \in \mathcal{P}^{M,N}$ be a rational
polynomial $\frac{P_n}{P_d} : P_n \in \mathcal{P}^{M} \wedge P_d \in
\mathcal{P}^{N}$.  There is a vector of coefficients
%
\begin{equation}
\vec{P} \in \mathbb{R}^{N+M+2}=[n_{0}\ n_{1}\ \hdots \ n_{M}\ d_{0}\ d_{1}\ \hdots\ d_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
%
with uncertainty
%
\begin{equation}
\Delta{\vec{P}}=[\Delta{n}_{0}\ \Delta{n}_{1}\ \hdots \ \Delta{n}_{M}\ \Delta{d}_{0}\ \Delta{d}_{1}\ \hdots\ \Delta{d}_{N}\ ]^T
\label{eq:coefficients}
\end{equation}
%
Then $\vec{\hat{G}}=\vec{G}+\Delta{\vec{G}}$.  In the following we may use
either notation to represent the functions $G(z)$, $C(z)$, and their
respective uncertainties.\\

@@

The ADC and DAC may be abstracted changing the hybrid system in
figure~\ref{fig:sampledsystem} to the digital system in
figure~\ref{fig:digsystem1} where the parametric uncertainties are
represented by $\Delta_p \vec{G}$
%
%=\mathcal{Z}\left\lbrace{G_{P}(s)}\right\rbrace$
%
and the entire effect of $\nu_{1}$ and $\nu_{2}$ in the output $Y(z)$ is
represented as an additive (output) measurement noise $\nu(z)$, thus
$\hat{Y}(z)=Y(z)+\nu(z)$.  The measurement noise $\nu(k)$ is enough for
represent both quantization noises ($\nu_{1}$ and $\nu_{2}$) what can be
obtained reorganizing the equations~\ref{eq:outputfunctions}:
%
\begin{equation}
\label{eq:outputfunctions2}
\hat{Y}(z)=H_{1}R(z)+H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z),
\end{equation}
%
where $H_{1}R(z)$ is exactly equal to $Y(z)$ without quantization noise effects, thus:
%
\begin{equation}
\nu(z)=H_{1}\nu_{1}(z)+H_{2}(z)\nu_{2}(z).
\end{equation}

@@

%
In figure~\ref{fig:digsystem1}, two sources of uncertainties are considered: parametric uncertainties related to modelling errors, and uncertainties introduced by quantisations in sampling and holding process, {\it i.e.} ADC and DAC conversions. Assuming linearity and independence between these sources, the uncertain model may be rewritten as follows:
\begin{equation}
\label{eq:complete_unc_model}
\vec{\hat{G}}=\vec{G}+\Delta_p \vec{G}+\Delta_q \vec{G},
\end{equation}
%
where $\Delta_p \vec{G}$ is the term that corresponds to the parametric uncertainties and $\Delta_q \vec{G}$ is the term that reflects the quantisation effects on the plant model. %\red{[next figure is a bit unnecessary, does not ad much to the previous one.]} Figure~\ref{fig:digsystem2} shows the digital closed loop systems with $\Delta G_{P}(z)$ and $\Delta G_{Q}(z)$.
